GSE158422: DNA methylation in Lung squamous cell carcinoma

### 2022-05-18 GSE158433/GSE158422.Rmd
progress on GSE158422.Rmd

SERIES_MATRIX="GSE158422_series_matrix.txt.gz"
download.file("ftp://ftp.ncbi.nlm.nih.gov/geo/series/GSE158nnn/GSE158422/matrix/GSE158422_series_matrix.txt.gz", 
  destfile=SERIES_MATRIX)
gse <- getGEO(filename=SERIES_MATRIX)
baseDir <- "."
sample_metadata <- pData(phenoData(gse))
targets <- sample_metadata
mybase <- unique(gsub("_Red.idat.gz" ,"",  gsub("_Grn.idat.gz", "" ,list.files(".",pattern = "GSM",recursive = TRUE))))
targets$Basename <- mybase
head(targets)
rgSet <- read.metharray.exp(targets = targets)
rgSet

@@

>>>>

SERIES_MATRIX="GSE158422_series_matrix.txt.gz"
if(!file.exists(SERIES_MATRIX)){
download.file("ftp://ftp.ncbi.nlm.nih.gov/geo/series/GSE158nnn/GSE158422/matrix/GSE158422_series_matrix.txt.gz", 
  destfile=SERIES_MATRIX)
}
gse <- getGEO(filename=SERIES_MATRIX)
baseDir <- "."
sample_metadata <- pData(phenoData(gse))
targets <- sample_metadata
mybase <- unique(gsub("_Red.idat.gz" ,"",  gsub("_Grn.idat.gz", "" ,list.files(".",pattern = "GSM",recursive = TRUE))))
targets$Basename <- mybase
head(targets)
rgSet <- read.metharray.exp(targets = targets)
rgSet

@@

saveRDS(GSE158422,file="GSE158422.rds")
write.table(GSE158422,file="GSE158422_limma.tsv",sep="\t",quote=FALSE)
